### 2014-12-26 mcmc.tex
tweak

The M--H MCMC algorithm is the following:
We have generated some set of samples, the most recent of which is $\pars_k$
To generate the next sample $\pars_{k+1}$ do the following:
\begin{itemize}
\item Draw a proposal $\pars'$ from the proposal disribution $p(\pars'\given\pars_k)$.
\item Draw a random number $0<r<1$ from the uniform distribution.
\item If $p(\pars') / p(\pars_k) > r$ then $\pars_{k+1} \leftarrow \pars'$;
      otherwise $\pars_{k+1} \leftarrow \pars_k$.
\end{itemize}
That is, at each step, either a new proposed position in the parameter
  space gets accepted or else the prior position in the parameter space
  gets repeated.
The algorithm can be iterated a large number $K$ of times to produce $K$ samples.

>>>>

The M--H MCMC algorithm is the following:
We have generated some set of samples, the most recent of which is $\pars_k$
To generate the next sample $\pars_{k+1}$ do the following:
\begin{itemize}
\item Draw a proposal $\pars'$ from the proposal disribution $p(\pars'\given\pars_k)$.
\item Draw a random number $0<r<1$ from the uniform distribution.
\item If $p(\pars') / p(\pars_k) > r$ then $\pars_{k+1} \leftarrow \pars'$;
      otherwise $\pars_{k+1} \leftarrow \pars_k$.
\end{itemize}
That is, at each step, either a new proposed position in the parameter
  space gets accepted into the list of samples or else the prior sample
  in the parameter space gets repeated.
The algorithm can be iterated a large number $K$ of times to produce $K$ samples.
